%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Lead Software Developer} % Job title
    {Freelance} % Organisation
    {Chapel Hill, UNC} % Location
    {Jan 2023 - Sep 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 6 undergraduate developers to create a sales representative management platform that received \textbf{200+ users} from the first launch week.}
        \item {Employed a \textbf{serverless} approach, leveraging \textbf{HTML}, \textbf{CSS}, \textbf{VanillaJS}, and \textbf{WebPack} for the frontend, along with \textbf{Firebase} to manage \textbf{hosting}, \textbf{authentication}, and \textbf{NoSQL} database management}
        \item {Transitioned the project to \textbf{React} post-launch to enhance user experience and performance.}
        \item {Introduced release management processes and automated deployment through \textbf{Github}, resulting in improved collaboration and efficient delivery.}
        \item {Conducted weekly \textbf{scrum meetings}, \textbf{code reviews}, and \textbf{tech talks} to ensure task transparency, on-time deliveries, and knowledge sharing for accelerated development.}
      \end{cvitems}
    }

    \cventry
    {Software Engineer} % Job title
    {Cymantix} % Organisation
    {North Carolina (hybrid), USA} % Location
    {Oct 2021 - Feb 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with a team of five developers to create a \textbf{full-stack SaaS machine-learning driven platform} that integrated a WebRTC video conferencing app, an information retrieval app, and a core identity API. The platform played a vital role in securing seed-round funding.}
        \item {Investigated using \textbf{Scikit-learn} of \textbf{Hierarchical clustering} as a replacement for the \textbf{K-Means}, reducing computation overhead by \textbf{10\%-60\%}.}
        \item {Incorporated \textbf{Microsoft Azure} into our platform, enhancing login options and facilitating seamless secured data transfer between our data retrieval app and Microsoft's cloud storage.}
        \item {Refactored codebase from \textbf{HTML}, \textbf{CSS}, and \textbf{in-line JavaScript} to \textbf{Next.js}, resulting in improved readability and \textbf{20\%} reduction in code redundancy.}
        \item {Optimized real-time news analysis process on the data retrieval platform using \textbf{multi-processing} and \textbf{Socket.io}, achieveing a \textbf{90\%} acceleration.}
        \item {Strengthened the critical data update pipeline with \textbf{Bash script}, \textbf{Python}, and \textbf{CronJob}, ensuring reliable and up-to-date PubMed data}
        % \item {\textbf{Technical Skills:} Flask, React, CronJob, Pandas, Scikit-learn, Apache Server, Google Cloud Platform, Microsoft Azure, Git.}
        % \item {\textbf{Soft Skills:} Teamwork, Work Life Balance, Communication, Scrum meetings.}
      \end{cvitems}
    }

    \cventry
    {Full Stack Developer Intern} % Job title
    {IBM} % Organisation
    {North Carolina (remote), USA} % Location
    {May 2021 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhanced user experience on a development environment management platform for \textbf{12000+} IBMers each month by implementing intuitive improvements based on user feedback.}
        \item {Rapidly acquired proficiency in  \textbf{NextJS}, \textbf{SailsJS}, and \textbf{MongoDB} within a week, enabling independent code contributions after two weeks.}
        \item {Streamlined administrative content activities, resulting in faster content updates and a reduction of \textbf{20+} redeployments per week for developers.}
        \item {Co-founded an automated validation service with a fellow intern using \textbf{SailsJS} to simplify employee database maintenance, saving \textbf{three months'} worth of manual operations annually.}
        \item {Collaborated effectively with cross-functional team members, including product managers, fellow developers, mentors, and UI/UX design engineers.}
        % \item {\textbf{Technical Skills:} Next.js, Sails.js, Git, Bash}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication.}
      \end{cvitems}
    }

    % \cventry
    % {Research Assistant} % Job title
    % {Laboratory of Applied Information Science at UNC - Chapel Hill} % Organisation
    % {North Carolina, USA} % Location
    % {Apr 2021 - Apr 2023} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {Established data visualization using Tableau for UNICEF to monitor the health conduction of children and women across 200 countries.}
    %     \item {Initiated a mobile application for a health data exchange platform using React Native and Flask Backend.}
    %     % \item {\textbf{Technical Skills:} Flask, React, React Native, Tableau, Pandas, , Google Cloud Platform, MySQL, Git.}
    %     % \item {\textbf{Soft Skills:} Teamwork, Work Life Balance, Communication, Presentations, documentation writing, demo videos}
    %   \end{cvitems}
    % }

    % \cventry
    % {UI/UX Engineer Intern} % Job title
    % {Lenovo} % Organisation
    % {Beijing, China} % Location
    % {Jun 2017 - Aug 2017} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {Designed Lenovo's B2B web store with Mocking-Bot (similar to Adobe XD), providing retailers with access to product information for over 1000 products and remote technology support and restocking capabilities.}
    %     \item {Negotiated with the marketing and human resources departments to determine the necessary resources to complete the project.}
    %     % \item {\textbf{Technical Skills:} Flask, React, React Native, Tableau, Pandas, , Google Cloud Platform, MySQL, Git.}
    %     % \item {\textbf{Soft Skills:} Teamwork, Work Life Balance, Communication, Presentations, documentation writing, demo videos}
    %   \end{cvitems}
    % }
\end{cventries}
