%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Machine Learning Backend Engineer} % Job title
    {ByteDance} % Organisation
    {Jan 2024 - Present} % Date(s)
    {San Jose, CA, USA} % Location
    {A member of IT's Enterprise Solution AI Operations Algorithm Team}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a Text-to-SQL AI agent with \textbf{LangChain} to automate natural language-to-SQL queries, integrated \textbf{RAG} for schema fetching, and enhanced ByteDance’s network monitoring service, saving \textbf{hundreds of human hours monthly} across all offices by streamlining network diagnostics.}
        \item {Developed and fine-tuned \textbf{computer vision} algorithms using \textbf{YOLO} for human detection, \textbf{DeepSort} for people tracking, and \textbf{Mmpos} for action detection to automate server room monitoring across \textbf{1,000+} global sites. The system triggers alerts for unauthorized access, over-crowding, or prohibited activities, eliminating manual monitoring and freeing up resources for server room management.}
        \item {Designed and implemented a network diagnostic AI chatbot for a commercialized ByteDance product based on \textbf{Swarm}. The chatbot enables non-technical users to diagnose network issues by retrieving and analyzing monitoring data, streamlining deployment for small businesses and reducing reliance on network specialists.}
        \item {Developed backend services using \textbf{FastAPI} (for Text-to-SQL and Network Diagnostic) and \textbf{gRPC} (for Computer Vision) to expose machine learning models and support client interaction. Implemented \textbf{authentication}, \textbf{managed deployment}, and ensured service health. Led real-time output \textbf{streaming} to enhance user experience and provide instant feedback.
        }
        \item {Collaborate with clients, product managers, and team members to clarify requirements, manage expectations, suggest alternative engineering solutions when needed, and brainstorm optimal approaches, ensuring clear communication and alignment across all stakeholders.}
      \end{cvitems}
    }
  % \cventry
  %   {Lead Software Engineer (Part Time)} % Job title
  %   {ChampionPDI} % Organisation
  %   {Jan 2023 - Sep 2023} % Date(s)
  %   {North Carolina, USA} % Location
  %   {Created and launched a powerful sales representative management platform for Cutco.}
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Led a team of 6 developers to launch a sales representative management platform that gained 200+ users in the first week.}
  %       \item {Initiated weekly scrum meetings, code reviews, and tech talks, which reduced learning costs and enabled all developers to contribute quality code after just 1 month.}
  %       \item {Delivered a production-quality web application within just 2 months using \textbf{HTML}, \textbf{CSS}, \textbf{JavaScript}, and \textbf{WebPack} for frontend and \textbf{Firebase} backend.}
  %       \item {Transitioned the project to \textbf{React} post-launch, which reduced database queries by 60\% and reduced loading speed by 50\%.}
  %       % \item {Introduced release management processes and automated deployment through \textbf{Github}, which saved 4 hours weekly in resolving code conflicts and rolling out bug fixes.}
  %     \end{cvitems}
  %   }

    \cventry
    {Software Engineer (Part Time)} % Job title
    {Cymantix} % Organisation
    {Oct 2021 - Feb 2023} % Date(s)
    {North Carolina, USA} % Location
    {A SaaS tech startup that integrated machine learning with data analytics and information retrieval.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Identified and resolved \textbf{communication issues} proactively between clients and engineers, which boosted the company's reputation and gained 3 additional clients.}
        \item {Investigated replacing K-Means with Hierarchical clustering on the \textbf{Flask (Python)} backend, which reduced computation and user wait time by 10\%-60\%.}
        \item {Optimized real-time news analysis using \textbf{multithreading}, \textbf{NodeJS} and \textbf{Socket.io}, which decreased user wait time by 90\%.}
        \item {Created a full-stack machine-learning-driven data analytics web platform in a global team of 5 engineers that secured seed-round funding.}
        \item {Refactored codebase to \textbf{Next.js} and added animations using \textbf{D3.js}, which reduced 20\% code redundancy and provided a smoother user experience.}
        \item {Integrated \textbf{Microsoft Azure} into our platform, which provided login options and secure data storage from Microsoft's cloud. Resulted in a cost-effective transition for users and gained 2 non-profit organizations as clients within 1 week.}
        \item {Automated PubMed data update pipeline using \textbf{Bash script}, \textbf{Python}, and \textbf{CronJob}, which reduced manual labor and gained 2 clients that required the most up to date data.}
      \end{cvitems}
    }

    \cventry
    {Full-Stack Engineer (Summer Intern)} % Job title
    {IBM} % Organisation
    {May 2021 - Aug 2021} % Date(s)
    {North Carolina, USA} % Location
    {Worked on IBM's internal platform that provisions and customizes live demo environments.}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-founded an automated validation service using \textbf{SailsJS} that streamlined database maintenance and saved the team \$14,000 annually by eliminating headcounts for manual tasks.}
        \item {Enhanced user experience based on user feedback using \textbf{NextJS}, which expanded the monthly user base to over 12,000+.}
        \item {Streamlined administrative content processes, achieved faster content updates, and reduced redeployments by over 20 per week.}
        % \item {Collaborated effectively with cross-functional team members, including product managers, fellow developers, mentors, and UI/UX design engineers.}
      \end{cvitems}
    }

    % \cventry
    % {Research Assistant} % Job title
    % {Laboratory of Applied Information Science at UNC - Chapel Hill} % Organisation
    % {North Carolina, USA} % Location
    % {Apr 2021 - Apr 2023} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {}
    %     \item {Initiated a mobile application for a health data exchange platform using React Native and Flask Backend.}
    %     % \item {\textbf{Technical Skills:} Flask, React, React Native, Tableau, Pandas, , Google Cloud Platform, MySQL, Git.}
    %     % \item {\textbf{Soft Skills:} Teamwork, Work Life Balance, Communication, Presentations, documentation writing, demo videos}
    %   \end{cvitems}
    % }

    % \cventry
    % {UI/UX Engineer Intern} % Job title
    % {Lenovo} % Organisation
    % {Beijing, China} % Location
    % {Jun 2017 - Aug 2017} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {Designed Lenovo's B2B web store with Mocking-Bot (similar to Adobe XD), providing retailers with access to product information for over 1000 products and remote technology support and restocking capabilities.}
    %     \item {Negotiated with the marketing and human resources departments to determine the necessary resources to complete the project.}
    %     % \item {\textbf{Technical Skills:} Flask, React, React Native, Tableau, Pandas, , Google Cloud Platform, MySQL, Git.}
    %     % \item {\textbf{Soft Skills:} Teamwork, Work Life Balance, Communication, Presentations, documentation writing, demo videos}
    %   \end{cvitems}
    % }
\end{cventries}
