%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Tech Lead / Product Manager} % Job title
    {Cutco/ChampionPDI} % Organisation
    {Chapel Hill, UNC} % Location
    {Jan 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 6 undergraduate developers to create a sales representative management platform that received \textbf{200+ users} from the first launch week.}
        \item {Designed the project to use the \textbf{serverless} approach for faster development lifecycles and lower learning curve.}
        \item {Used \textbf{HTML}, \textbf{CSS}, \textbf{VanillaJS}, and \textbf{WebPack} for the web front end, and \textbf{Firebase} to manage hosting, authentication, and a NoSQL database.}
        \item {Transitioned to using \textbf{React} for the front end after the initial release for a faster user experience.}
        \item {Introduced the release management process for better collaboration and created automated deployment using \textbf{Github Actions}.}
        \item {Held weekly scrum meetings and code reviews to ensure all team members were transparent with their tasks and could deliver on time. Also held \textbf{tech talks} to introduce new technologies and tools for faster development process.}
      \end{cvitems}
    }

    \cventry
    {Software Engineer} % Job title
    {Cymantix} % Organisation
    {North Carolina (hybrid), USA} % Location
    {Oct 2021 - Feb 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered, with a team of five developers, a \textbf{full-stack SaaS machine-learning driven platform} that integrated a WebRTC video conferencing app, an information retrieval app, and a core identity API. The platform played a crucial role in the company securing seed-round funding.}
        % \item {Created the personal dataset upload feature involvin?g frontend support, NER, and elastic search indexing.}
        \item {Explored with researchers and developers on the team to replace the \textbf{K-Means} algorithm with \textbf{Hierarchical clustering} to reduce redundant computation overhead.}
        \item {Incorporated \textbf{Microsoft Azure} into our platform per our client's request, providing more flexible login choices and enabling seamless secured data transfer between our data retrieval app and Microsoft's cloud storage.}
        % \item {Refactored the codebase and transitioned from pure \textbf{HTML}, \textbf{CSS}, and \textbf{in-line JavaScript} to \textbf{Next.js}}
        \item {Parallelize our data retrieval platform's real-time news analysis process using \textbf{ThreadPoolExecutor} and \textbf{Socket.io}, leading to a \textbf{90\%} acceleration.}
        \item {Strengthened our critical data update pipeline using \textbf{bash script}, \textbf{python}, and \textbf{CronJob}, increasing reliability and ensuring our Pubmed data is always up to date.}
        % \item {\textbf{Technical Skills:} Flask, React, CronJob, Pandas, Scikit-learn, Apache Server, Google Cloud Platform, Microsoft Azure, Git.}
        % \item {\textbf{Soft Skills:} Teamwork, Work Life Balance, Communication, Scrum meetings.}
      \end{cvitems}
    }

    \cventry
    {Full Stack Developer Intern} % Job title
    {IBM} % Organisation
    {North Carolina (remote), USA} % Location
    {May 2021 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved user experience on a development environment management platform that supports \textbf{2000+} IBM developers each month. The improvements are based on user feedback to provide a more intuitive experience.}
      \item {Learned \textbf{NextJS}, \textbf{SailsJS}, and \textbf{MongoDB} in a week and started contributing to the code base independently after two weeks.}
        \item {Streamlined administrative content activities to reduce workload for developers, resulting in faster content updates and \textbf{20+} fewer required redeployments per week.}
        \item {Founded an automated validation service with a fellow intern using \textbf{SailsJS} that simplifies maintaining the employee database, reducing \textbf{3 months'} worth of manual operations each year.}
        \item {Collaborated closely with all other team members, including the product manager, other developers, my mentor, and the UI/UX design engineer.}
        % \item {\textbf{Technical Skills:} Next.js, Sails.js, Git, Bash}
        % \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication.}
      \end{cvitems}
    }

    % \cventry
    % {Research Assistant} % Job title
    % {Laboratory of Applied Information Science at UNC - Chapel Hill} % Organisation
    % {North Carolina, USA} % Location
    % {Apr 2021 - Apr 2023} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {Established data visualization using Tableau for UNICEF to monitor the health conduction of children and women across 200 countries.}
    %     \item {Initiated a mobile application for a health data exchange platform using React Native and Flask Backend.}
    %     % \item {\textbf{Technical Skills:} Flask, React, React Native, Tableau, Pandas, , Google Cloud Platform, MySQL, Git.}
    %     % \item {\textbf{Soft Skills:} Teamwork, Work Life Balance, Communication, Presentations, documentation writing, demo videos}
    %   \end{cvitems}
    % }

    % \cventry
    % {UI/UX Engineer Intern} % Job title
    % {Lenovo} % Organisation
    % {Beijing, China} % Location
    % {Jun 2017 - Aug 2017} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {Designed Lenovo's B2B web store with Mocking-Bot (similar to Adobe XD), providing retailers with access to product information for over 1000 products and remote technology support and restocking capabilities.}
    %     \item {Negotiated with the marketing and human resources departments to determine the necessary resources to complete the project.}
    %     % \item {\textbf{Technical Skills:} Flask, React, React Native, Tableau, Pandas, , Google Cloud Platform, MySQL, Git.}
    %     % \item {\textbf{Soft Skills:} Teamwork, Work Life Balance, Communication, Presentations, documentation writing, demo videos}
    %   \end{cvitems}
    % }
\end{cventries}
